\textbf{Hardware accelerator topologies in heterogeneous systems: an evaluation in the security domain}

### 2019-12-08 reports/paper.tex
add a bit of interpretation

% TODO small interpretation paragraph here

>>>>

% TODO small interpretation paragraph here
The hybrid accelerator is significantly faster than all other implementations
tested. This is to be expected since the accelerator itself performs the memory
requests without intervention of the CPU, directly into the memory bus. The
memory-mapped accelerator in the automatic mode comes in as second fastest. This
is also to be expected in comparison with the RoCC accelerator for example,
since the latter is run in interactive mode, that is, the application code
issues each round sequentially and sequential rounds are not immediately
executed by the CPU, due to buffering and communication logic in the RoCC
adapter fabric, in contrast to the former where rounds occur immediately (next
clock cycle) one after the other.

% superscalar also
